simon_test_loop

### 2019-03-26 src/stack_test.Rmd
happy with maxent model fiddling.

mod11 <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=4", "replicatetype=boo", "replicates=10")) 
mod11

@@

@@

#aic fiddling

@@

>>>>

mod11 <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=4", "replicates=10")) #replicates added
mod11

@@

#probably dont want replicates - no real way to merge the outputs. saw somehting online that said ideally you want to run just one model

@@

mod12 <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=4", "addsamplestobackground=TRUE")) #add to samples because field study with biased data - see https://esajournals.onlinelibrary.wiley.com/doi/10.1890/10-1171.1. note this should be the default but keep here as a note
mod12

pre12 <- predict(mod12, test, args='outputformat=logistic' ) 
preplot12 <- plot(pre12)
preplot12

#ok think i am good. the think you will want to change is the beta value - depending on the results of the AIC and when you figure out the test/training data partion, will need to add testsamplesfile

#AIC for regularization

```{r}
#aic fiddling

@@

write.csv(AIClist, "../output/bio/AICforMaxentReg.csv", row.names = FALSE)
```
